---
title: "Statistical Inference Project Part 2"
author: "Bryan Willauer"
date: "4/25/2020"
output: html_document
---

## Data Summary ##

The data comes from an experiment on the effect of vitamin C on tooth growth in Guinea Pigs. The data is
formatted as a data frame with 60 observations of three variables.

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Name  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  Type  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;   Description
   
1. len  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  numeric  &nbsp;&nbsp;&nbsp; tooth length

2. supp  &nbsp;&nbsp;&nbsp; factor  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  supplement type (vitamin C VC or orange Juice OJ)

3. dose  &nbsp;&nbsp;&nbsp; numeric &nbsp;&nbsp; dose in mg/day


```{r message=FALSE, warning=FALSE}
library(tidyverse)
data("ToothGrowth")
str(ToothGrowth)
head(ToothGrowth)
summary(ToothGrowth)
```



## Exploratory Data Analysis ##

```{r}
ToothGrowth %>% ggplot(aes(as.factor(dose),len, fill = supp)) +
        facet_grid(.~ supp) +
        geom_boxplot() +
        labs(x = "Dose", y = "Length") +
        ggtitle("Figure #1: Tooth Length By Dose Per Supplement")
```

Preliminary analysis seems to show that tooth length increases with increasing dosages of both supplements.
Howeever, lower doses of Orange Juice look to do better that the lower doses of Vitamin C.


## Hypothesis Testing ##

The following t-test tests the null hypothesis that there is a difference in length due to choice of supplement,

```{r}
t.test(ToothGrowth$len ~ ToothGrowth$supp)
```

The following t-tests test whether there is a difference dosages of each supplement. The data was split into three groups,
 each goup contins the individual does so we can compare how each supplement at each dose compares. The first test tests the
 0.5mg/day dosage. 

```{r}
dose0.5 <- subset(ToothGrowth, ToothGrowth$dose==c(0.5))
dose2 <- subset(ToothGrowth, ToothGrowth$dose==c(2))
dose1   <- subset(ToothGrowth, ToothGrowth$dose==c(1))
t.test(dose0.5$len ~ dose0.5$supp, paired = FALSE, var.equal = FALSE)
```

The second test tests the 1mg/day dosage.

```{r}
t.test(dose1$len ~ dose1$supp, paired = FALSE, var.equal = FALSE)
```

the third test tests the 2mg/day dosage.

```{r}
t.test(dose2$len ~ dose2$supp, paired = FALSE, var.equal = FALSE)
```


## Conclusion ##

The first t-test, where we tested the null hypothesis of no difference between using either supplement resulted in not being
able to reject the null hypothesis. The p-value was above .05 and the 95% confidence interval contained zero. 

The tests related to the dosage of the supplement resulted in being able to reject the null hypothesis of no difference in 
supplements at the same dosage for the two lower dosages. Both tests for the two lower dosages had low p-values, high t 
values, and 95% confidence intervals not containg zero. Thus the smaller dosages showed significant tooth length difference 
when orange juice was supplemented rather than vitamin C. We could nor reject the null hypothesis at the higher dosage. The
p-value was high and the 95% confidence interval contained zero. So there was no significant difference between the supplemets
at 2mg/day.



