---
title: "Statistical Inference Project Part 2"
author: "Bryan Willauer"
date: "4/25/2020"
output: html_document
---

## Data Summary ##

The data comes from an experiment on the effect of vitamin C on tooth growth in Guinea Pigs. The data is
formatted as a data frame with 60 observations of three variables.

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Name  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  Type  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;   Description
   
1. len  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  numeric  &nbsp;&nbsp;&nbsp; tooth length

2. supp  &nbsp;&nbsp;&nbsp; factor  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  supplement type (vitamin C VC or orange Juice OJ)

3. dose  &nbsp;&nbsp;&nbsp; numeric &nbsp;&nbsp; dose in mg/day


```{r message=FALSE, warning=FALSE}
library(tidyverse)
data("ToothGrowth")
str(ToothGrowth)
head(ToothGrowth)
summary(ToothGrowth)
```



## Exploratory Data Analysis ##

```{r}
ToothGrowth %>% ggplot(aes(as.factor(dose),len, fill = supp)) +
        facet_grid(.~ supp) +
        geom_boxplot() +
        labs(x = "Dose", y = "Length") +
        ggtitle("Figure #1: Tooth Length By Dose Per Supplement")
```

Preliminary analysis seems to show that tooth length increases with increasing dosages of both supplements.
Howeever, lower doses of Orange Juice look to do better that the lower doses of Vitamin C.


## Hypothesis Testing ##



## Conclusion ##